---
title: "eds221_day1_handout"
author: "carly"
format: html
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(ggplot2)
```

```{r}
## Reading in Data
stl_lead <- read_csv(here::here("data","stl_lead.csv")) %>% 
  clean_names()
```

```{r}
## Basic Data Exploration
head(stl_lead)
dim(stl_lead)
skim(stl_lead)
```

Create a new data frame called stl_lead_prop that has one additional column called prop_white that returns the percent of each census tract identifying as white (variable white in the dataset divided by variable totalPop, times 100).

```{r}
stl_lead_prop <- stl_lead %>%  dplyr::mutate(prop_white = (white/total_pop) * 100)
```

Scatterplot graph of the percentage of children in each census tract with elevated blood lead levels (pctElevated) versus the percent of each census tract identifying as white:

```{r}
stl_lead_plot <-
ggplot(data = stl_lead_prop, aes(x = prop_white, y = pct_elevated)) + geom_point(aes(color = poverty_tot, alpha = 4, size = 6))
stl_lead_plot
```

```{r}
ggsave(here::here("figs", "stl_lead_plot.png"), height = 6, width = 7)

```

### My findings:

The elevated pct levels are much higher when the population of white individuals is much lower. In addition, the poverty total amounts seem to be most prevalent where the proportion of white individuals is lower, noticeably 50% or lower.

-   Create a histogram of only the `pctElevated` column in the data frame (remember, this will only take one variable - the frequency is calculated for you by `geom_histogram`)

-   Customize the fill, color, and size aesthetics - test some stuff! Feel free to make it awful.

-   Once you've played around with customization, export the histogram as a .jpg to the `figs` folder

-   Make sure the histogram also shows up in your rendered html

```{r}
ggplot(data = stl_lead, aes(x= pct_elevated)) + geom_histogram(fill = "magenta", aes(bins = 6))
```

```{r}
ggsave(here::here("figs", "pct_elevated_plot.jpg"), height = 6, width = 7)

```
